---
title: "Project Presentation Work"
author: "Nikhil Gudipally, Prajakta Ghumatkar, Sindhya Balasubramanian, Vishnu Rohan"
date: "12/6/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Phase 1 - Read Files and EDA
```{r EDA}
#setwd("C:/Users/Shivapriya B/Desktop/NEU Work/Classwork/Semester 1/IDMP/Project Presentation and Report/Data")
df <- read.csv("~/Downloads/netflix-rotten-tomatoes-metacritic-imdb.csv")
View(df)
#check number of NAs in rotten tomatoes score
print(sum(is.na(df$Rotten.Tomatoes.Score)))

#check number of NAs in IMDB score
print(sum(is.na(df$IMDb.Score)))

#check number of NAs in rotten tomatoes score and IMDB score
print(sum(is.na(df$IMDb.Score) && is.na(df$Rotten.Tomatoes.Score)))

#Create new Score attribute by combining IMDB score and rotten tomatoes score
library(dplyr)
library(tidyr)
df <- df %>% 
  mutate(Score = if_else(is.na(IMDb.Score)==FALSE, IMDb.Score, Rotten.Tomatoes.Score/10))
print(sum(is.na(df$Score)))
df = df %>% drop_na(Score)

#Deleting Rotten.Tomatoes.Score and IMDb.Score as it is replaced by Score
df = subset(df, select = -c(Rotten.Tomatoes.Score,IMDb.Score))

#Deleting Columns with a lot of missing data
df = subset(df, select = -c(Metacritic.Score,Awards.Nominated.For, Awards.Received))
```

Phase 2 - Tidying the data
```{r}
temp = select(df, c(Title, Genre, Languages, Series.or.Movie, Hidden.Gem.Score, Country.Availability, Runtime, Director, Writer, Actors, Boxoffice, Score));
temp = separate_rows(temp, Languages);

temp[!is.na(temp$Languages),]
temp %>% distinct();
temp = separate_rows(temp, Genre);
temp[!is.na(temp$Genre),]
temp %>% distinct();
temp = separate_rows(temp, Actors);
temp[!is.na(temp$Actors),]
temp %>% distinct();
temp = separate_rows(temp, Director);
temp[!is.na(temp$Director),]
temp %>% distinct();
temp = separate_rows(temp, Writer);
temp[!is.na(temp$Writer),]
temp %>% distinct();

head(temp)
```

Phase 3 - Visualizations
a. Language level analysis of ratings
```{r}
library(ggplot2)
temp = df
temp = separate_rows(temp, Languages)

langScore <- temp %>% distinct() %>% group_by(Languages) %>% summarise(Score = mean(Score), count=n()) 
langScore <- langScore %>% arrange(desc(count))
langScore1 <- head(langScore[,],10)

otherScore = langScore[11:196,2]
otherCount = langScore[11:196,3]

others <- data.frame("Others", mean(otherScore$Score), sum(otherScore$Score))
names(others) = c("Languages", "Score", "count")
langScore1 = rbind(langScore1,others)

ggplot(langScore1, aes(x=Languages, y=Score)) + 
  geom_bar(stat = "identity", fill='blue') +  
  labs(x='Language') + labs(y='Rating') + 
  theme_minimal()
```
b. Genre Distribution for Series and Movies
```{r}
library(ggplot2)
df_1 = temp %>%
  select(c(Title, Genre)) %>%
  distinct() %>%
  group_by(Genre) %>%
  count ()

ggplot(data = df_1, mapping = aes(x = Genre, y = n)) +
  geom_col(fill = 'blue') +
  theme_minimal() +
  scale_x_discrete(guide = guide_axis(angle = 90)) + 
  labs (x = "Genre", y = "Count Series & Movies")
```
c. Genre Distribution for Series
```{r}
df_1 = temp %>%
  filter(Series.or.Movie == "Series") %>%
  select(c(Title, Genre)) %>%
  distinct() %>%
  group_by(Genre) %>%
  count ()

ggplot(data = df_1, mapping = aes(x = Genre, y = n)) +
  geom_col(fill = 'blue') +
  theme_minimal() +
  scale_x_discrete(guide = guide_axis(angle = 90)) + 
  labs (x = "Genre", y = "Count Series")
```

d. Genre Distribution for  Movies
```{r}
df_1 = temp %>%
  filter(Series.or.Movie == "Movie") %>%
  select(c(Title, Genre)) %>%
  distinct() %>%
  group_by(Genre) %>%
  count ()

df_1
ggplot(data = df_1, mapping = aes(x = Genre, y = n)) +
  geom_col(fill = 'blue') +
  theme_minimal() +
  scale_x_discrete(guide = guide_axis(angle = 90)) + 
  labs (x = "Genre", y = "Count Movies")
```
e. Language Distribution for Series
```{r}
df_1 = temp %>%
  filter(Series.or.Movie == "Series") %>%
  select(c(Title, Languages)) %>%
  distinct() %>%
  group_by(Languages) %>%
  count () %>%
  arrange(desc(n))

df_1 = df_1[!is.na(df_1$Languages), ]
df_1 = df_1[1:10,]
  
ggplot(data = df_1, mapping = aes(x = Languages, y = n)) +
  geom_col(fill = 'blue') +
  theme_minimal() +
  scale_x_discrete(guide = guide_axis(angle = 90)) + 
  labs (x = "Languages", y = "Count Series")
```
f. Language Distribution for Movies
```{r}
df_1 = temp %>%
  filter(Series.or.Movie == "Movie") %>%
  select(c(Title, Languages)) %>%
  distinct() %>%
  group_by(Languages) %>%
  count () %>%
  arrange(desc(n))

df_1 = df_1[!is.na(df_1$Languages), ]
df_1 = df_1[1:10,]
  
ggplot(data = df_1, mapping = aes(x = Languages, y = n)) +
  geom_col(fill = 'blue') +
  theme_minimal() +
  scale_x_discrete(guide = guide_axis(angle = 90)) + 
  labs (x = "Languages", y = "Count Movie")
```
g. Distribution of shows and movies as individual categories 
```{r}
ggplot(df, aes(x=reorder(Series.or.Movie, Series.or.Movie, function(x)-length(x)))) +
  geom_bar(fill='blue') +  
  labs(x='Category') + labs(y='Count') + 
  theme_minimal()
```


Phase 4 - Dimension Reduction 
a. t-SNE for Non Linear Relationships

Step 1 - Calcualte Gower Distance
```{r}
library(cluster)
temp$Genre <- as.factor(temp$Genre)
temp$Actors <- as.factor(temp$Actors)
temp$Languages <- as.factor(temp$Languages)
temp$Director <- as.factor(temp$Director)

df_1 = select(temp, c(Title,Genre, Actors, Languages, Score)) %>%
  distinct()
df_1$Title = as.factor(df_1$Title)
df_2 = select(df_1, c(Title,Genre, Actors, Languages, Score)) %>%
  distinct()

tmp_df = sample_n(df_2, 5000) 
head(tmp_df)

rm(df_1)

gower_df = daisy(tmp_df,
                metric = "gower");
```

Step 2 - tSNE using Perplexity 10
```{r}
set.seed(1)
rm(temp)
library(Rtsne)

tsne_1 <- Rtsne(gower_df, perplexity=10, verbose=FALSE, max_iter = 10000)

color_table = tmp_df$Genre;
colnames(tsne_1$Y) <- c("C1", "C2")
X_10 = as.data.frame(tsne_1$Y)

ggplot(X_10, aes(x=C1, y=C2, color = color_table)) +
  geom_point() +
  scale_color_brewer(palette="Dark2") +
  labs(title="Perplexity = 10") +
  theme_minimal()
```

Step 2 - tSNE using Perplexity 30
```{r}
set.seed(1)

tsne <- Rtsne(gower_df, perplexity=30, verbose=FALSE, max_iter = 10000)

colnames(tsne$Y) <- c("C1", "C2")
X_30 = as.data.frame(tsne$Y)

ggplot(X_30, aes(x=C1, y=C2, color = color_table)) +
  geom_point() +
  scale_color_brewer(palette="Dark2") +
  labs(title="Perplexity = 30") +
  theme_minimal()
```

Step 3 - tSNE using Perplexity 50
```{r}
set.seed(1)

tsne_3 <- Rtsne(gower_df, perplexity=50, verbose=FALSE, max_iter = 10000)

colnames(tsne_3$Y) <- c("C1", "C2")
X_50 = as.data.frame(tsne_3$Y)

ggplot(X_50, aes(x=C1, y=C2, color = color_table)) +
  geom_point() +
  scale_color_brewer(palette="Dark2") +
  labs(title="Perplexity = 50") +
  theme_minimal()
```